Efficient GPU implementation of multicomponent and multiphase Lattice Boltzmann models.

### 2010-04-28 paper.tex
Add Q_iab definition, rewrap a few paragraphs.

The lattice Boltzmann equation operates on the rectangular grid representing the physical domain. It utilizes the probability distribution functions containing the information about the macroscopic variables, such as density, momentum. LBE consists from two parts: local collision and propagation operated from one node to another in the certain direction specified by the velocity set.  The lattice Boltzmann implementation in a standard view representing the collision and propagation steps:
\begin{equation}
\label{standard:implementation}
\begin{aligned}
&f_i^{*}(\bm{x},t)=\omega f_i^{eq}(\bm{x},t)-(1-\omega) f_i(\bm{x},t) + F_i,&&\text{ collision step}\\
&f_i(\bm{x}+\bm{c_i},t+1)=f_i^{*}(\bm{x},t),&&\text{ propagation step}, 
\end{aligned}
\end{equation}
where $F_i$ is the external force population. The equilibrium function population is usually given as \cite{}:
\begin{equation}
f_i^{eq}=w_i \rho \biggl(1+\frac{c_{i\alpha}u_{\alpha}}{c_s^2}+\frac{Q_{i\alpha\beta}u_{\alpha}u_{\beta}}{2 c_s^4}\biggr),
\end{equation}
where for D2Q9 $w_i=\{\dfrac{4}{9},\dfrac{1}{9},\dfrac{1}{9},\dfrac{1}{9},\dfrac{1}{9},\dfrac{1}{36},\dfrac{1}{36},\dfrac{1}{36},\dfrac{1}{36}\}$ and $Q_{i\alpha\beta}=$ with the sound speed parameter $c_s^2=\dfrac{1}{3}$. The macroscopic variables are restored on every time step through the probability function population:
\begin{equation*}
\begin{aligned}
&\rho=\sum_i{f_i}
&\rho u_{\alpha}=\sum_i{f_i c_{i\alpha}}
\end{aligned}
\end{equation*}
The multiphase models can be simulated either through the force population and/or special equilibrium function. The Shan-Chen model utilizes the force population, but the free-energy model is simulated through the special equilibrium model. Both models are described in the next sections.

>>>>

The lattice Boltzmann equation operates on the rectangular grid representing the physical domain. It utilizes the
probability distribution functions containing the information about the macroscopic variables, such as density,
momentum. LBE consists from two parts: local collision and propagation operated from one node to another in the certain
direction specified by the velocity set.  The lattice Boltzmann implementation in a standard view representing the
collision and propagation steps:
\begin{equation}
\label{standard:implementation}
\begin{aligned}
&f_i^{*}(\bm{x},t)=\omega f_i^{eq}(\bm{x},t)-(1-\omega) f_i(\bm{x},t) + F_i,&&\text{ collision step}\\
&f_i(\bm{x}+\bm{c_i},t+1)=f_i^{*}(\bm{x},t),&&\text{ propagation step}, 
\end{aligned}
\end{equation}
where $F_i$ is the external force population. The equilibrium function population is usually given as \cite{}:
\begin{equation}
f_i^{eq}=w_i \rho \biggl(1+\frac{c_{i\alpha}u_{\alpha}}{c_s^2}+\frac{Q_{i\alpha\beta}u_{\alpha}u_{\beta}}{2 c_s^4}\biggr),
\end{equation}
where for D2Q9
$w_i=\{\dfrac{4}{9},\dfrac{1}{9},\dfrac{1}{9},\dfrac{1}{9},\dfrac{1}{9},\dfrac{1}{36},\dfrac{1}{36},\dfrac{1}{36},\dfrac{1}{36}\}$
and $Q_{i\alpha\beta}=c_{i\alpha} c_{i\beta} - c_s^2 \delta_{\alpha\beta}$ with the sound speed parameter $c_s^2=\dfrac{1}{3}$. The macroscopic variables are restored on
every time step through the probability function population:
\begin{equation*}
\begin{aligned}
&\rho=\sum_i{f_i}
&\rho u_{\alpha}=\sum_i{f_i c_{i\alpha}}
\end{aligned}
\end{equation*}
The multiphase models can be simulated either through the force population and/or special equilibrium function. The
Shan-Chen model utilizes the force population, but the free-energy model is simulated through the special equilibrium
model. Both models are described in the next sections.
